SAT Competition 2020\tnoteref{title}

### 2021-02-04 paper/main.tex
added some missing cites

The Parallel track evaluates the runtime performance in wall-clock time of SAT solvers making use of
 multiple processor cores.
The benchmarks and the timeout (5000 seconds) are the same as in the Main track \textcolor{red}{repetitive? also mentioned below?}. 
Each solver in this track was run on a m4.16xlarge machine from Amazon Web Services (AWS).
These machines have 64 virtual cores and 256GB of memory. In contrast to the 
Main track, proof logging for unsatisfiable instances is not required in the Parallel track.

@@

New this year was the Cloud track, dedicated to evaluating distributed solvers \textcolor{red}{Not sure
if terms ``distributed'' vs ``parallel'' are clear, could be more explicitly explained?}. Similar to the
Parallel track, the solvers ran on the Amazon cloud, but using 100 machines of the
type m4.4xlarge, which have 16 virtual cores and 64GB of memory. 
Communication between the machines is possible using MPI and SSH.
The wall-clock timeout is 1000 seconds and the same benchmarks were used as in
the Main and Parallel track. \textcolor{red}{repetitive? also mentioned below?}

@@

\label{sec:computing}
The Main, No-Limits, and Planning tracks were run on the StarExec cluster \cite{starexec}
with computing nodes  equipped with Intel Xeon \SI{2.4}{\giga\hertz} processors 
and \SI{128}{\giga\byte} of memory.
The time limit enforced on each solver for solving an instance was \SI{5000}{\second}. 
(In the Main track, validation then continued for up to \SI{45000}{\second}.)
The solvers were allowed to use the full \SI{128}{\giga\byte} of RAM.\footnote{
Unfortunately, the memory limit of \SI{24}{\giga\byte}, that was used in the previous years,
was by mistake advertised on the competition web page prior to solver submission.
This could have resulted in some solvers not ``daring'' to use the full \SI{128}{\giga\byte}
in the competition.}

The Incremental Library Track was run on computers with 2x Intel Xeon E5430 \SI{2.66}{\giga\hertz}
(4-Core) processors and \SI{24}{\giga\byte} of RAM.

As noted above, the Parallel track was run on AWS m4.16xlarge machines with 64 virtual CPUs and 256 GB
of memory, while the Cloud track was run on AWS m4.4xlarge machines with 16 virtual CPUs and 64 GB of
memory. These tracks used wall-clock timeouts of \SI{5000}{\second} and \SI{1000}{\second}, respectively.

@@

\textcolor{red}{global note: should try to be consistent with present/past tense...}

@@

The classical planning benchmarks were selected from the \emph{satisfying} and
\emph{Optimal} tracks of the \emph{International Planning Competitions} 2014
\footnote{\url{https://helios.hud.ac.uk/scommv/IPC-14/repository/benchmarksV1.1.zip}}
and 2018 \footnote{\url{https://bitbucket.org/ipc2018-classical/domains}}.

In addition to the classical planning problems, we also included SAT formulas
generated by \emph{Tree-REX} \cite{TreeRex19}; a planner for \emph{Hierarchical
  Task-networks}. In HTN planning the planner is provided with additional domain
knowledge besides the problem description. The HTN benchmarks were provided by
the author of \emph{Tree-REX}.

@@

The main reason for the separation between the top-4 solvers and the others is the noticeable gap on satisfiable benchmarks, 
see Figure~\ref{main:sat}. In recent years, several techniques have been added to SAT solvers to improve
their performance on satisfiable instance. Examples of such techniques are the integration of a local search
solver and alternating between a SAT mode (infrequent restarts) and an UNSAT mode (frequent restarts
and variable-move-to-front \textcolor{red}{screams for a reference...}). The 2020 winner of the Main SAT track is \solver{Relaxed-newTech}, followed by
\solver{Kissat-sat} and \solver{CMS-ccnr-lsids}.

@@

Another, more recent line of development in SAT solvers
is rooted in the \solver{CoMinisatPS} fork of \solver{Minisat} by Oh which introduced three-tier clause-management~\cite{Oh:2015:satunsat}. 
The SAT solver \solver{Maple} appeared as a series of forks presenting innovative branching heuristics at SAT Competition 2016~\cite{Liang:2016:LRB}. 
The then award-winning variant \solver{MapleCOMSPS} by Liang et al.~is an implementation of a hybrid branching heuristic of classic variable-state independent decaying sum (VSIDS)\textcolor{red}{add ref} and the newer learning rate based branching (LRB) in \solver{CoMinisatPS}~\cite{Liang:2016:MapleCOMSPS}.

>>>>

The Parallel track evaluates the runtime performance in wall-clock time of SAT solvers making use of multiple processor cores.
The benchmarks %and the timeout (5000 seconds) 
are the same as in the Main track. 
%\textcolor{red}{repetitive? also mentioned below?}. 
%Each solver in this track was run on a m4.16xlarge machine from Amazon Web Services (AWS).
%These machines have 64 virtual cores and 256GB of memory. 
However, in contrast to the Main track, proof logging for unsatisfiable instances is not required in the Parallel track.

@@

New this year was the Cloud track, dedicated to evaluating distributed solvers running on multiple machines in a network. 
%\textcolor{red}{Not sure if terms ``distributed'' vs ``parallel'' are clear, could be more explicitly explained?}. 
%Similar to the Parallel track, the solvers ran on the Amazon cloud, but using 100 machines of the type m4.4xlarge, which have 16 virtual cores and 64GB of memory. 
Communication between the machines is possible using MPI and SSH.
%The wall-clock timeout is 1000 seconds and the same benchmarks were used as in the Main and Parallel track. \textcolor{red}{repetitive? also mentioned below?}

@@

\label{sec:computing}
The Main, No-Limits, and Planning tracks were run on the StarExec cluster \cite{starexec}
with computing nodes  equipped with Intel Xeon \SI{2.4}{\giga\hertz} processors 
and \SI{128}{\giga\byte} of memory.
The time limit enforced on each solver for solving an instance was \SI{5000}{\second}. 
(In the Main track, validation then continued for up to \SI{45000}{\second}.)
The solvers were allowed to use the full \SI{128}{\giga\byte} of RAM.\footnote{
Unfortunately, the memory limit of \SI{24}{\giga\byte}, that was used in the previous years,
was by mistake advertised on the competition web page prior to solver submission.
This could have resulted in some solvers not ``daring'' to use the full \SI{128}{\giga\byte}
in the competition.}
The Incremental Library Track was run on computers with 2x Intel Xeon E5430 \SI{2.66}{\giga\hertz}
(4-Core) processors and \SI{24}{\giga\byte} of RAM.

%As noted above, 
The Parallel track was run on AWS m4.16xlarge machines with 64 virtual CPUs and 256 GB
of memory, while the Cloud track was run on AWS m4.4xlarge machines with 16 virtual CPUs and 64 GB of
memory. These tracks used wall-clock timeouts of \SI{5000}{\second} and \SI{1000}{\second}, respectively.

@@

%\textcolor{red}{global note: should try to be consistent with present/past tense...}

@@

The classical planning benchmarks were selected from the \emph{Satisfying} and
\emph{Optimal} tracks of the \emph{International Planning Competitions} 2014
\footnote{\url{https://helios.hud.ac.uk/scommv/IPC-14/repository/benchmarksV1.1.zip}}
and 2018 \footnote{\url{https://bitbucket.org/ipc2018-classical/domains}}.
In addition to the classical planning problems, we also included SAT formulas
generated by \emph{Tree-REX} \cite{TreeRex19}; a planner for \emph{Hierarchical
  Task-networks}. In HTN planning the planner is provided with additional domain
knowledge besides the problem description. The HTN benchmarks were provided by
the author of \emph{Tree-REX}.

@@

The main reason for the separation between the top-4 solvers and the others is the noticeable gap on satisfiable benchmarks, 
see Figure~\ref{main:sat}. In recent years, several techniques have been added to SAT solvers to improve
their performance on satisfiable instance. Examples of such techniques are the integration of a local search
solver and alternating between a SAT mode (infrequent restarts) and an UNSAT mode (frequent restarts
and variable-move-to-front~\cite{Ryan:2004:Thesis}). The 2020 winner of the Main SAT track is \solver{Relaxed-newTech}, followed by
\solver{Kissat-sat} and \solver{CMS-ccnr-lsids}.

@@

Another, more recent line of development in SAT solvers
is rooted in the \solver{CoMinisatPS} fork of \solver{Minisat} by Oh which introduced three-tier clause-management~\cite{Oh:2015:satunsat}. 
The SAT solver \solver{Maple} appeared as a series of forks presenting innovative branching heuristics at SAT Competition 2016~\cite{Liang:2016:LRB}. 
The then award-winning variant \solver{MapleCOMSPS} by Liang et al.~is an implementation of a hybrid branching heuristic of classic variable-state independent decaying sum (VSIDS)~\cite{Zhang:2001:ClauseLearning} and the newer learning rate based branching (LRB) in \solver{CoMinisatPS}~\cite{Liang:2016:MapleCOMSPS}.
